---
title: "p8105_hw1_ha2546"
author: "Hana Akbarnejad"
date: "9/13/2019"
output: github_document
---

```{r library, include = FALSE}

library(tidyverse)

```


# problem 1

## 1-1
First, I am going to create a data frame containing a random sample and different vectors. On the next step, I have calculated the mean of each variable in my data frame.


```{r create_df_mean}

prob1_df = tibble(
  vec_sample = rnorm(8),
  vec_logic = vec_sample > 0,
  vec_char = c("This", "is", "problem", "one", "homework", "one", "Hana", "Akbarnejad"),
  vec_factor = factor(c("good", "fair", "poor", "poor", "fair", "fair", "fair", "fair"))
)

sample_mean = mean(pull(prob1_df, vec_sample))
sample_mean
logic_mean = mean(pull(prob1_df, vec_logic))
logic_mean
char_mean = mean(pull(prob1_df, vec_char))
char_mean
factor_mean = mean(pull(prob1_df, vec_factor))
factor_mean

```

* **Results**

When trying to calculate the mean for the variables in my data frame, I observed that it is not possible for character and factor arguments. Calculating mean is only possible for numeric or logical vectors.


## 1-2
In the second part, I have tried to convert the logical, character, and factor variables' types I had to numeric:

```{r transform_to_numeric, results='hold'}

num_logic = as.numeric(pull(prob1_df, vec_logic))
num_logic
num_char = as.numeric(pull(prob1_df, vec_char))
num_char
num_factor = as.numeric(pull(prob1_df, vec_factor))
num_factor

```

* **Results**

It was observed that we were unable to convert character vector to numeric. However, logical and factor vectors were converted to numeric form. That is the reason why we were unable to take the mean for character vector. We also can conclude that we cannot take the mean of factor vectors as they are, but we are able to convert them to numeric form and then take the mean.


## 1-3
On the final step for question one, I played a little bit with the logical vector! First, I did some calculations with the logical vector that I had just converted to numeric in the last part. Then, I converted the logical vector to factor, and tried to do calculations, then converted it to numeric again, and done some calculations.

Then, I have converted the logical vector again, but this time to a factor vector. And again, done some calculations...


```{r playing_with_logic!}

num_logic_calc = pull(prob1_df, vec_sample) * num_logic
num_logic_calc

factor_logic = as.factor(pull(prob1_df, vec_logic))
factor_logic_calc1 = pull(prob1_df, vec_sample) * factor_logic
factor_logic
factor_logic_calc1

num_factor_logic = as.numeric(factor_logic)
factor_logic_calc2 = pull(prob1_df, vec_sample) * num_factor_logic
num_factor_logic
factor_logic_calc2

```

 * **Results**

It can be observed that calculations are possible when dealing with logical vector after it was transformed to numeric but it is not possible when we convert it to factor (which was expected due to previous parts). Also, when we saw that transforming factors to numerics is possible, so we are able to do calculations when we convert the factor to numeric. 
 
# Problem 2

## 2.1
First, I am going to creat a data frame, define varian=bles x and y, and a logical vector. Then I transformed the logical vector to numeric and factor.

```{r create_df_2}

prob2_df = tibble(
  x = rnorm(500),
  y = rnorm(500),
  prob2_logic = x + y > 1
)

num_logic2 = as.numeric(pull(prob2_df, prob2_logic))
factor_logic2 = as.factor(pull(prob2_df, prob2_logic))

```

The size of my dataset is `r dim(prob2_df)`; which means it has `r nrow(prob2_df)` rows and `r ncol(prob2_df)`columns. The mean of x is `r mean(pull(prob2_df, x))`, its median is `r median(pull(prob2_df, x))`, and its standard deviation is `r sd(pull(prob2_df, x))`. The proportion of cases for which x + y > 1 is `r length(which (num_logic2 == 1)) / (nrow(prob2_df) * ncol(prob2_df))`

## 2.2
In this part, I have made three scatter plots and colored the points using 1- logical variable, 2- numeric variable, and 3- factor variable.

```{r scatter_plots}

logic_scatterplot = ggplot(prob2_df, aes(x = x, y = y, color = prob2_logic)) + geom_point()
logic_scatterplot

num_logic_scatterplot = ggplot(prob2_df, aes(x = x, y = y, color = num_logic2)) + geom_point()
num_logic_scatterplot

factor_logic_scatterplot = ggplot(prob2_df, aes(x = x, y = y, color = factor_logic2)) + geom_point()
factor_logic_scatterplot

ggsave("logic_scatterplot2.pdf")

```

* Results(comment on colors in these three plots)
........

