---
title: "p8105_hw1_ha2546"
author: "Hana Akbarnejad"
date: "9/13/2019"
output: github_document
---

```{r}

library(tidyverse)

```


# problem 1

## 1-1.
First, I am going to create a data frame containing a random sample and different vectors, and on the next step, I have calculated the mean of each variable inmy data frame. Then, I have converted logical, character, and factor variables' types to numeric:


```{r}

prob1_df = tibble(
  vec_sample = rnorm(8),
  vec_logic = vec_sample > 0,
  vec_char = c("This", "is", "problem", "one", "homework", "one", "Hana", "Akbarnejad"),
  vec_factor = factor(c("good", "fair", "poor", "poor", "fair", "fair", "fair", "fair"), ordered = TRUE)
)

sample_mean = mean(pull(prob1_df, vec_sample))
logic_mean = mean(pull(prob1_df, vec_logic))
char_mean = mean(pull(prob1_df, vec_char))
factor_mean = mean(pull(prob1_df, vec_factor))

num_logic = as.numeric(pull(prob1_df, vec_logic))
num_char = as.numeric(pull(prob1_df, vec_char))
num_factor = as.numeric(pull(prob1_df, vec_factor))

```

* Results:
 

## 1-2.
In the second part, I have taken the logical variable that I had converted to numeric, and do some calculations. Then, I have converted the logical vector again, but this time to a factor variable. And again, done some calculations...

```{r}

num_logic_calc = pull(prob1_df, vec_sample) * num_logic

factor_logic = as.factor(pull(prob1_df, vec_logic))
factor_logic_calc1 = pull(prob1_df, vec_sample) * factor_logic

num_factor_logic = as.numeric(factor_logic)
factor_logic_calc2 = pull(prob1_df, vec_sample) * num_factor_logic

```

 * Results:
 ............
 
# Problem 2


 
 
 

